---
title: "Report"
author: "Jamie Stankiewiz"
date: "October 13, 2016"
output: pdf_document
---
# Abstract


# Introduction

# Data
```{r}

ad <- read.csv('../data/Advertising.csv')

```


\bigskip
\begin{center}
Simple regression of Sales on Radio
\end{center}
```{r}

coefficients(summary(lm(Sales ~ Radio, data= ad)))
```

\bigskip
\begin{center}
Simple regression of Sales on Newspaper
\end{center}
```{r}

coefficients(summary(lm(Sales ~ Newspaper, data=ad)))

```

\bigskip
\begin{center}
Simple regression of Sales on TV
\end{center}
```{r}

coefficients(summary(lm(Sales ~ TV, data = ad)))
```

\begin{center}
Correlation Matrix:
\end{center}
```{r}

corrmat <- round(cor(ad[2:5]),4)
corrmat[lower.tri(corrmat)] <- NA
corrmar

```

\begin{center}
Coefficient estimates of the least squares model
\end{center}
```{r}

round(summary(lm(Sales ~ TV+Radio+Newspaper , data=ad))$coefficients, 3)
```




```{r pressure, echo=T}
plot(pressure)
```


# Methodology

# Results


This table refers to the least squares model statistics for the multiple regression.
```{r}

regdata <- summary(lm(Sales ~ TV+Radio+Newspaper , data=ad))
values <- c(round(regdata$sigma,3), round(regdata$r.squared, 3), round(regdata$fstatistic, 3)[1])
names <- c('Residual standard error', 'R-squared', 'F-statistic')
matvals <- matrix(c(names,values), nrow=3, ncol=2)
df <- as.data.frame(matvals, row.names=NA, col.names=c('Quantity', 'Value'))
colnames(df) <- c('Quantity', 'Values')
df

```

\bigskip
1) Is at least one of the predictors useful in predicting the response?
  The ANOVA test compares all of the \beta_0 values to check if they all are equal to zero. This let's us check to see if there's a difference between any given mean in a pairwise fashion.  Since our F-statistic corresponds to a very small p-value, we can reject the null hypothesis (\H_0).  Therefore, we can conclude that at least one of the predictors is useful in predicting the response.

\bigskip

2) Do all predictors help to explain the response, or is only a subset of the predictors useful?

\bigskip  

3) How well does the model fit the data?
  To see how well the model fits the data, we look at the $R^2$ test statistic.  $R^2$ tells us how well the data fits the regression model.  Here, our $R^2$ value is 
```{r}
summary(lm(Sales ~ TV+Radio+Newspaper , data=ad))$r.squared
```
You can see that is value is closer to 1 than it is to 0, meaning that the regression model is explained very much so by the predictors.

\bigskip

4) How accurate is the prediction?





# Conclusions

